---
title: "Annex A: Analysis of Queue Time & Service Times"
subtitle: "SGH PAC Data (2020--2021)"
date: "Sunday, 11 April 2021"
author: "Vincent Leonardo"
output:
  pdf_document:
    highlight: tango
    latex_engine: xelatex
    number_sections: true
    toc: true
fontsize: 11pt
geometry: margin=1in
mainfont: Bookerly
mathfont: STIX Two Math
monofont: Fira Code
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
# Remove all variables from the R environment to create a fresh start
rm(list=ls())
# Execute our custom script for loading packages
source("Functions/usePackages.R")
# Name of the packages 
pkgnames <- c("ggplot2","dplyr","GGally","fmsb","tidyverse","knitr","lubridate",
              "patchwork", "fitdistrplus")
# Use our custom load function
loadPkgs(pkgnames)

source("Functions/2020_PAC_initial_cleaner.R")
source("Functions/histogram_maker.R")
source("Functions/cf_graph.R")
source("Functions/find_dist.R")
# source("Functions/chi_squared_exp.R")
source("Functions/chi_squared_tests.R")
source("Functions/2021_PAC_planned_initial_cleaner.R")

theme_set(
  theme_light() + theme(legend.position = "top")
  )
```

\newpage

# Introduction

In forming our queuing model for SGH PAC, the role and aim in this section is to extract distributions for these two variables:

1.  *Queueing time*. This is the variable that indicates the amount of time taken between the arrival of a patient and the consult with the anaesthesiologist.
2.  *Service time*. This is the variable that indicates the amount of time taken in a consult with the anaesthesiologist.

The data given to us is from 2019 to 2021 for both planned appointments and walk-in appointments. However, we will only focus on data from 2020 onwards due to SGH's claim that the 2019 data may not be as reliable.

# Assumptions

Acknowledging that the real world data may not be ideal, we would like to lay down some assumptions regarding the data that will help with the model-fitting.

1.  There is no exact data for queueing time. Therefore, it will be assumed that the queueing time is the total duration that the patient is in PAC subtracted by the actual consult duration. Implicitly, the other PAC stations (e.g. Radiology) where patients are assessed are considered as a "queue" in this case. For our purposes, this decision is justified as the project focuses on the anaesthesiologists and the consults thereof.
2.  That any service time below 15 minutes is considered a data error. We must also acknowledge the assumption that any data above that is fully accurate to a reasonable degree, except when in the case that it is unrealistically high.

# Methodology

This is a mostly quantitative analysis. The data will be cleaned, meaning that any data error will be removed, and appropriate data types shall be applied to each variable. Data from 2020 and 2021 will then be aggregated into two tibbles (in essence, a better version of a data frame for R), one for planned appointments and walk-in appointments. There will be eight tibbles formed through this split, knowing that ASA Scores range from 1 to 4. However, there may not be enough data to form a distribution for the ASA Score of 4 due to its rarity.

The eight tibbles will be analysed using descriptive statistics in the beginning, and then we will try to fit likely distributions to it. Ideally, the distributions will all be exponential. The main test that will be done to corroborate the distribution and its parameters will be the chi-squared test at $\alpha$ = 0.05.

# Data Cleaning

## Raw Data

### 2020 Planned Appointments

```{r}
raw_planned_2020 <- read_csv("Unedited CSV/2020_planned.csv")

head(raw_planned_2020)
```

### 2020 Walk-In Appointments

```{r}
raw_walk_in_2020 <- read_csv("Unedited CSV/2020_add_on.csv")

head(raw_walk_in_2020)
```

### 2021 Planned Appointments

```{r}
raw_planned_2021 <- read_csv("Unedited CSV/2021_planned.csv")

head(raw_planned_2021)
```

### 2021 Walk-In Appointments

```{r}
raw_walk_in_2021 <- read_csv("Unedited CSV/2021_add_on.csv")

head(raw_walk_in_2021)
```

\newpage

## Cleaned Data

### Planned Appointments Aggregate

```{r}
initial_planned_2020 <- PAC_initial_cleaner("Unedited CSV/2020_planned.csv")
initial_planned_2021 <- PAC_2021_initial_planned_cleaner("Unedited CSV/2021_planned.csv")

planned_appointments <- tibble(
  asa = c(
    initial_planned_2020$asa,
    initial_planned_2021$asa
  ),
  queue_time = c(
    initial_planned_2020$PAC_queue_time,
    initial_planned_2021$PAC_queue_time
  ),
  consult_duration = c(
    initial_planned_2020$PAC_consult_duration,
    initial_planned_2021$PAC_consult_duration
  ),
  month = c(
    month(initial_planned_2020$PAC_register_date_time),
    month(initial_planned_2021$PAC_register_date_time)
  )
)

planned_appointments <- planned_appointments %>% 
  filter(asa != "#N/A")

head(planned_appointments)
```

```{r}
asa_integer <- planned_appointments %>% mutate(asa = as.integer(asa))
summary_planned <- summary(asa_integer)
kable(summary_planned, col.names = c("ASA Score", "Queue Time", "Consult Duration", "Month"),
      caption = "Descriptive statistics for planned appointments")
```

```{r fig.cap="Histogram for queuing time for appointments in PAC"}
ggplot(planned_appointments) + geom_histogram(aes(queue_time), bins = 45) +
  facet_wrap(~asa, scales = 'free_y') +
  theme_minimal() +
  labs(
    title = "Histogram for Queue Times for Appointments in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Queue Time",
    y = "Count",
    color = "ASA Score"
  )
```

```{r fig.cap="Histogram for consult duration for appointments in PAC"}
ggplot(planned_appointments) + 
  geom_histogram(aes(consult_duration), bins = 50) +
  facet_wrap(~asa, scales = 'free_y') +
  theme_minimal() +
  labs(
    title = "Histogram for Consult Duration for Appointments in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

Seeing the histogram for consult duration, it might be a bit more useful to think of it as the amount of time beyond 15 minutes the consult will take. Hence, we will translate the consult duration by 15 minutes to the left.

```{r fig.cap="Histogram for adjusted consult duration for appointments in PAC"}
ggplot(planned_appointments) + 
  geom_histogram(aes(consult_duration-15), bins = 50) +
  facet_wrap(~asa, scales = 'free_y') +
  theme_minimal() +
  labs(
    title = "Histogram for Adjusted Consult Duration for Appointments in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

\newpage

### Walk-In Appointments Aggregate

```{r}
initial_add_on_2020 <- PAC_initial_cleaner("Unedited CSV/2020_add_on.csv")
initial_add_on_2021 <- PAC_initial_cleaner("Unedited CSV/2021_add_on.csv")
initial_add_on_2020 <- initial_add_on_2020 %>% 
  mutate(PAC_duration_total = PAC_duration_total/60,
         PAC_queue_time = PAC_duration_total - PAC_consult_duration)

add_on_appointments <- tibble(
  asa = c(
    initial_add_on_2020$asa,
    initial_add_on_2021$asa
  ),
  queue_time = c(
    initial_add_on_2020$PAC_queue_time,
    initial_add_on_2021$PAC_queue_time
  ),
  consult_duration = c(
    initial_add_on_2020$PAC_consult_duration,
    initial_add_on_2021$PAC_consult_duration
  ),
  month = c(
    month(initial_add_on_2020$PAC_register_date_time),
    month(initial_add_on_2021$PAC_register_date_time)
  )
)

add_on_appointments <- add_on_appointments %>% 
  filter(asa != "#N/A")

head(add_on_appointments)
```

```{r}
asa_integer_1 <- add_on_appointments %>% mutate(asa = as.integer(asa))
summary_add_on <- summary(asa_integer_1)
kable(summary_add_on, col.names = c("ASA Score", "Queue Time", "Consult Duration", "Month"),
      caption = "Descriptive statistics for walk-in appointments")
```

Similarly to the planned appointments, the three figures below describe the queue time and consult duration in histograms.

```{r fig.cap="Histogram for queuing time for walk-ins in PAC"}
ggplot(add_on_appointments) + 
  geom_histogram(aes(queue_time), bins = 30) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Queue Times for Walk-Ins in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Queue Time",
    y = "Count",
    color = "ASA Score"
  )
```

```{r fig.cap="Histogram for consult duration for walk-ins in PAC"}
ggplot(add_on_appointments) + 
  geom_histogram(aes(consult_duration), bins = 30) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Consult Duration for Walk-Ins in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

```{r fig.cap="Histogram for adjusted consult duration for walk-ins in PAC"}
ggplot(add_on_appointments) + 
  geom_histogram(aes(consult_duration-15), bins = 30) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Adjusted Consult Duration for Walk-Ins in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

\newpage

### Appointments Aggregate

```{r}
appointments <- tibble(
  asa = c(
    planned_appointments$asa,
    add_on_appointments$asa
  ),
  queue_time = c(
    planned_appointments$queue_time,
    add_on_appointments$queue_time
  ),
  consult_duration = c(
    planned_appointments$consult_duration,
    add_on_appointments$consult_duration
  ),
  month = c(
    planned_appointments$month,
    add_on_appointments$month
  )
)

head(appointments)
```

```{r fig.cap="Histogram for queuing time in PAC"}
ggplot(appointments) + 
  geom_histogram(aes(queue_time), bins = 30) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Queue Times in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Queue Time",
    y = "Count",
    color = "ASA Score"
  )
```

```{r fig.cap="Histogram for consult duration in PAC"}
ggplot(appointments) + 
  geom_histogram(aes(consult_duration), bins = 30) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Consult Duration in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

```{r fig.cap="Histogram for adjusted consult duration in PAC"}
ggplot(appointments) + 
  geom_histogram(aes(consult_duration-15), bins = 25) +
  facet_wrap(~asa, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  labs(
    title = "Histogram for Adjusted Consult Duration in PAC",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "",
    x = "Consult Duration",
    y = "Count",
    color = "ASA Score"
  )
```

\newpage

### Counts Per Month

#### 2020

\

```{r fig.cap="Histogram for patient counts in 2020"}
ggplot(appointments[appointments$month!=1&appointments$month!=2&appointments$month!=3,]) + 
  geom_bar(aes(month)) +
  labs(
    title = "Bar Chart for the Number of Patients in 2020",
    subtitle = "From 1 July 2020 to 1 December 2020",
    caption = "Cleaned up data that will be used for distribution analysis",
    x = "Month",
    y = "Count"
  ) + theme_minimal()
```

#### 2021

\

```{r fig.cap="Histogram for patient counts in 2021"}
ggplot(appointments[appointments$month==1|appointments$month==2|appointments$month==3,]) + 
  geom_bar(aes(month)) +
  labs(
    title = "Bar Chart for the Number of Patients in 2021",
    subtitle = "From 1 January 2021 to 5 March 2021",
    caption = "Cleaned up data that will be used for distribution analysis",
    x = "Month",
    y = "Count"
  ) + theme_minimal()
```

#### Compared by ASA

\

```{r fig.cap="Counts by ASA"}
ggplot(appointments) + geom_bar(aes(asa)) +
  labs(
    title = "Patient Counts by ASA",
    subtitle = "From 1 July 2020 to 5 March 2021",
    caption = "Cleaned up data that will be used for distribution analysis",
    x = "ASA",
    y = "Count"
  ) + theme_minimal()
```

```{r}
asa_prob_table <- tibble(
  `ASA 1` = nrow(appointments[appointments$asa==1,])/nrow(appointments),
  `ASA 2` = nrow(appointments[appointments$asa==2,])/nrow(appointments),
  `ASA 3-4` = nrow(appointments[appointments$asa==3|appointments$asa==4,])/nrow(appointments)
)
kable(asa_prob_table, caption = "Ratio of Patients by ASA")
```

# Finding Distributions

## Planned and Walk-In Appointments

### Queue Time

#### ASA 1

\

```{r}
descdist(appointments[appointments$asa=="1",]$queue_time)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(appointments[appointments$asa=="1",]$queue_time,"lnorm", "mme")
# c("mle", "mme", "qme", "mge", "mse"))
```

\

```{r}
chi_squared_lnorm(
  appointments[appointments$asa=="1",],
  appointments[appointments$asa=="1",]$queue_time, 
  c(13, 100, 150, 200, 250, 300, Inf),
  4.7441447,
  0.4887809
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments[appointments$asa=="1",]$queue_time,"gamma", "mme")
# c("mle", "mme", "qme", "mge", "mse"))
```

```{r}
chi_squared_gamma(
  appointments[appointments$asa=="1",],
  appointments[appointments$asa=="1",]$queue_time, 
  c(13, 80, 120, 150, 200, 250, 300, Inf),
  3.70562271,
  0.02861722
)
```

#### ASA 2

\

```{r}
descdist(appointments[appointments$asa=="2",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments[appointments$asa=="2",]$queue_time,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  appointments[appointments$asa=="2",],
  appointments[appointments$asa=="2",]$queue_time,
  c(27, 125, 130, 135, 140, 145, 150, 155, 160, 165, 175, 225, 350, Inf),
  4.51396193,
  0.02991051
)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(appointments[appointments$asa=="2",]$queue_time,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  appointments[appointments$asa=="2",],
  appointments[appointments$asa=="2",]$queue_time,
  c(27, 125, 130, 135, 140, 145, 150, 155, 160, 165, 175, 225, 350, Inf),
  4.9116591,
  0.4419957
)
```

#### ASA 3

\

```{r}
descdist(appointments[appointments$asa=="3",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments[appointments$asa=="3",]$queue_time,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  appointments[appointments$asa=="3",],
  appointments[appointments$asa=="3",]$queue_time,
  c(27, 125, 130, 135, 140, 145, 150, 155, 160, 165, 175, 225, 350, Inf),
  4.4903452,
  0.0290352
)
```

### Consult Duration

Adjusted version, meaning that the consult duration was shifted by 15 minutes, unless otherwise stated.

#### ASA 1

\

```{r}
appointments_adj <- appointments %>% 
  mutate(consult_duration = consult_duration - 15)

appointments_adj_1 <- appointments %>% 
  mutate(consult_duration = consult_duration - 14)

```

```{r}
descdist(appointments_adj[appointments_adj$asa=="1",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(appointments_adj_1[appointments_adj_1$asa=="1",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  appointments_adj_1[appointments_adj_1$asa=="1",],
  appointments_adj_1[appointments_adj_1$asa=="1",]$consult_duration,
  c(1, 10, 20, 30, 40, 50, 60, 70, 80, 90, Inf),
  2.4525327,
  0.8756247
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="1",]$consult_duration,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  appointments_adj[appointments_adj$asa=="1",],
  appointments_adj[appointments_adj$asa=="1",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, Inf),
  0.76873108,
  0.04790915
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="1",]$consult_duration,"exp", "mme")

```

```{r}
chi_squared_exp(
  appointments_adj[appointments_adj$asa=="1",],
  appointments_adj[appointments_adj$asa=="1",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, Inf),
  0.06232238
)
```

#### ASA 2

\

```{r}
descdist(appointments_adj_1[appointments_adj_1$asa=="2",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(appointments_adj_1[appointments_adj_1$asa=="2",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  appointments_adj_1[appointments_adj_1$asa=="2",],
  appointments_adj_1[appointments_adj_1$asa=="2",]$consult_duration,
  c(1, 25, 50, 60, Inf),
  2.7364665,
  0.8274675
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="2",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  appointments_adj[appointments_adj$asa=="2",],
  appointments_adj[appointments_adj$asa=="2",]$consult_duration,
  c(0, 25, 50, 60, Inf),
  0.92565787,
  0.04464725
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="2",]$consult_duration,"exp", "mme")
```

```{r}
chi_squared_exp(
  appointments_adj[appointments_adj$asa=="2",],
  appointments_adj[appointments_adj$asa=="2",]$consult_duration,
  c(0, 25, 50, 60, Inf),
  0.048233
)
```

#### ASA 3

\

```{r}
descdist(appointments_adj_1[appointments_adj$asa=="3",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(appointments_adj_1[appointments_adj_1$asa=="3",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  appointments_adj_1[appointments_adj_1$asa=="3",],
  appointments_adj_1[appointments_adj_1$asa=="3",]$consult_duration,
  c(1, 10, 20, 30, 40, 50, 75, 100, Inf),
  3.0657644,
  0.8372545
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="3",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  appointments_adj[appointments_adj$asa=="3",],
  appointments_adj[appointments_adj$asa=="3",]$consult_duration,
  c(0, 25, 50, 75, 100, Inf),
  0.92089709,
  0.03126416
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(appointments_adj[appointments_adj$asa=="3",]$consult_duration,"exp", "mme")
```

```{r}
chi_squared_exp(
  appointments_adj[appointments_adj$asa=="3",],
  appointments_adj[appointments_adj$asa=="3",]$consult_duration,
  c(0, 25, 50, 75, 100, Inf),
  0.03394968
)
```

## Planned Appointments

### Queue Time

#### ASA 1

\

```{r}
descdist(planned_appointments[planned_appointments$asa=="1",]$queue_time)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(planned_appointments[planned_appointments$asa=="1",]$queue_time,"lnorm", "mme")
# c("mle", "mme", "qme", "mge", "mse"))
```

```{r}
chi_squared_lnorm(
  planned_appointments[planned_appointments$asa=="1",],
  planned_appointments[planned_appointments$asa=="1",]$queue_time, 
  c(13, 100, 150, 200, 250, 300, Inf),
  4.7362772,
  0.4766837
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments[planned_appointments$asa=="1",]$queue_time,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  planned_appointments[planned_appointments$asa=="1",],
  planned_appointments[planned_appointments$asa=="1",]$queue_time, 
  c(13, 100, 150, 200, 250, 300, Inf),
  3.91979880,
  0.03068901
)
```

#### ASA 2

\

```{r}
descdist(planned_appointments[planned_appointments$asa=="2",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments[planned_appointments$asa=="2",]$queue_time,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  planned_appointments[planned_appointments$asa=="2",],
  planned_appointments[planned_appointments$asa=="2",]$queue_time,
  c(27, 95, 100, 105, 110, 115, 120, 130, 140, 150, 160, 170, 180, 200, 350, Inf),
  4.6350196,
  0.0309402
)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(planned_appointments[planned_appointments$asa=="2",]$queue_time,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  planned_appointments[planned_appointments$asa=="2",],
  planned_appointments[planned_appointments$asa=="2",]$queue_time,
  c(27, 95, 100, 105, 110, 115, 120, 130, 140, 150, 160, 170, 180, 200, 350, Inf),
  4.9116591,
  0.4419957
)
```

#### ASA 3

\

```{r}
descdist(planned_appointments[planned_appointments$asa=="3",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments[planned_appointments$asa=="3",]$queue_time,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  planned_appointments[planned_appointments$asa=="3",],
  planned_appointments[planned_appointments$asa=="3",]$queue_time,
  c(47, 60, 70, 80, 100, 130, 150, 180, 200, 300, Inf),
  4.77692467,
  0.03145134
)
```

### Consult Duration

Adjusted version, meaning that the consult duration was shifted by 15 minutes, unless otherwise stated.

#### ASA 1

\

```{r}
planned_appointments_adj <- planned_appointments %>% 
  mutate(consult_duration = consult_duration - 15)

planned_appointments_adj_1 <- planned_appointments %>% 
  mutate(consult_duration = consult_duration - 14)

```

```{r}
descdist(planned_appointments_adj[planned_appointments_adj$asa=="1",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(planned_appointments_adj_1[planned_appointments_adj_1$asa=="1",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="1",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="1",]$consult_duration,
  c(1, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, Inf),
  2.456952,
  0.874598
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="1",]$consult_duration,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  planned_appointments_adj[planned_appointments_adj$asa=="1",],
  planned_appointments_adj[planned_appointments_adj$asa=="1",]$consult_duration,
  c(0, 20, 30, 40, 50, 60, 70, 80, 90, 100, Inf),
  0.7716552,
  0.0479119
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="1",]$consult_duration,"exp", "mme")

```

```{r}
chi_squared_exp(
  planned_appointments_adj[planned_appointments_adj$asa=="1",],
  planned_appointments_adj[planned_appointments_adj$asa=="1",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, Inf),
  0.06208978
)
```

#### ASA 2

\

```{r}
descdist(planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",]$consult_duration,
  c(1, 40, 50, 60, 100, Inf),
  2.7402942,
  0.8228612
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="2",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",]$consult_duration,
  c(0, 40, 50, 60, 100, Inf),
  0.9400198,
  0.0453387
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="2",]$consult_duration,"exp", "mme")
```

```{r}
chi_squared_exp(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="2",]$consult_duration,
  c(0, 40, 50, 60, 70, 80, 90, 100, Inf),
  0.04823165
)
```

#### ASA 3

\

```{r}
descdist(planned_appointments_adj_1[planned_appointments_adj$asa=="3",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",]$consult_duration,
  c(1, 15, 30, 45, 75, Inf),
  3.0717530,
  0.8440134
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="3",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",]$consult_duration,
  c(0, 25, 35, 45, 55, 65, 80, Inf),
  0.90118456,
  0.03022804
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(planned_appointments_adj[planned_appointments_adj$asa=="3",]$consult_duration,"exp", "mme")
```

```{r}
chi_squared_exp(
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",],
  planned_appointments_adj_1[planned_appointments_adj_1$asa=="3",]$consult_duration,
  c(0, 25, 35, 45, 55, 65, 80, Inf),
0.03354257
)
```

## Walk-In Appointments

### Queue Time

#### ASA 1

\

```{r}
descdist(add_on_appointments[add_on_appointments$asa=="1",]$queue_time)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(add_on_appointments[add_on_appointments$asa=="1",]$queue_time,"lnorm", "mme")
# c("mle", "mme", "qme", "mge", "mse"))
```

```{r}
chi_squared_lnorm(
  add_on_appointments[add_on_appointments$asa=="1",],
  add_on_appointments[add_on_appointments$asa=="1",]$queue_time, 
  c(16, 100, 150, 200, 250, 300, Inf),
  4.8384769,
  0.5555817
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments[add_on_appointments$asa=="1",]$queue_time,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  add_on_appointments[add_on_appointments$asa=="1",],
  add_on_appointments[add_on_appointments$asa=="1",]$queue_time, 
  c(16, 100, 150, 200, 250, 300, Inf),
  2.76537723,
  0.01876737
)
```

#### ASA 2

\

```{r}
descdist(add_on_appointments[add_on_appointments$asa=="2",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments[add_on_appointments$asa=="2",]$queue_time,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  add_on_appointments[add_on_appointments$asa=="2",],
  add_on_appointments[add_on_appointments$asa=="2",]$queue_time,
  c(28, 95, 100, 105, 110, 115, 120, 125, 130, 140, 150, 160, 170, 180, 200, 350, Inf),
  3.69937258,
  0.02254071
)
```

##### Testing for Lognormal Distribution

\

```{r}
find_dist(add_on_appointments[add_on_appointments$asa=="2",]$queue_time,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  add_on_appointments[add_on_appointments$asa=="2",],
  add_on_appointments[add_on_appointments$asa=="2",]$queue_time,
  c(28, 95, 100, 105, 110, 115, 120, 130, 140, 150, 160, 170, 180, 200, 350, Inf),
  4.980962,
  0.489148
)
```

#### ASA 3

\

```{r}
descdist(add_on_appointments[add_on_appointments$asa=="3",]$queue_time)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments[add_on_appointments$asa=="3",]$queue_time,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  add_on_appointments[add_on_appointments$asa=="3",],
  add_on_appointments[add_on_appointments$asa=="3",]$queue_time,
  c(49, 60, 70, 80, 100, 130, 150, 180, 200, 300, Inf),
  3.50311077,
  0.01894881
)
```

### Consult Duration

\

Adjusted version, meaning that the consult duration was shifted by 15 minutes, unless otherwise stated.

#### ASA 1

\

```{r}
add_on_appointments_adj <- add_on_appointments %>% 
  mutate(consult_duration = consult_duration - 15)

add_on_appointments_adj_1 <- add_on_appointments %>% 
  mutate(consult_duration = consult_duration - 14)

```

```{r}
descdist(add_on_appointments_adj[add_on_appointments_adj$asa=="1",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="1",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="1",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="1",]$consult_duration,
  c(1, 10, 20, 30, 40, Inf),
  2.4071329,
  0.8858606
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa=="1",]$consult_duration,"gamma", "mme")

```

```{r}
chi_squared_gamma(
  add_on_appointments_adj[add_on_appointments_adj$asa=="1",],
  add_on_appointments_adj[add_on_appointments_adj$asa=="1",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, Inf),
  0.74003981,
  0.04794076
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa=="1",]$consult_duration,"exp", "mme")

```

```{r}
chi_squared_exp(
  add_on_appointments_adj[add_on_appointments_adj$asa=="1",],
  add_on_appointments_adj[add_on_appointments_adj$asa=="1",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, Inf),
  0.06478132
)
```

#### ASA 2

\

```{r}
descdist(add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",]$consult_duration,
  c(1, 10, 20, 30, 40, 50, 60, 100, Inf),
  2.692986,
  0.878081
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa=="2",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",]$consult_duration,
  c(0, 20, 30, 40, 50, 60, 70, Inf),
  0.78319684,
  0.03778855
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa=="2",]$consult_duration,"exp", "mme")
```

```{r}
chi_squared_exp(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="2",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, 70, Inf),
  0.0482491
)
```

#### ASA 3

\

```{r}
descdist(add_on_appointments_adj_1[add_on_appointments_adj$asa=="3",]$consult_duration)
```

##### Testing for Lognormal Distribution

\

The lognormal distribution requires numbers above 0. Hence, the shifting in this case is by 14, such that the minimum is 1.

```{r}
find_dist(add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="3",]$consult_duration,"lnorm", "mme")
```

```{r}
chi_squared_lnorm(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="3",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="3",]$consult_duration,
  c(1, 15, 30, 45, 75, Inf),
  3.0349670,
  0.6988318
)
```

##### Testing for Gamma Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa=="3",]$consult_duration,"gamma", "mme")
```

```{r}
chi_squared_gamma(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="3",],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa=="3",]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, Inf),
  1.47081119,
  0.05755881
)
```

##### Testing for Exponential Distribution

\

```{r}
find_dist(add_on_appointments_adj[add_on_appointments_adj$asa == "3", ]$consult_duration, "exp", "mme")
```

```{r}
chi_squared_exp(
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa == "3", ],
  add_on_appointments_adj_1[add_on_appointments_adj_1$asa == "3", ]$consult_duration,
  c(0, 10, 20, 30, 40, 50, 60, Inf),
  0.03913405
)
```

# Summary and Conclusion

## Planned and Walk-In Appointments

### Queue Time

| ASA Score | Distribution                    |  Error   | Critical Values |
|:---------:|---------------------------------|:--------:|:---------------:|
|     1     | Lognormal(4.7441447, 0.4887809) | 3.790103 |    9.487729     |
|     2     | Gamma(4.51396193, 0.02991051)   | 17.96091 |    18.30704     |
|     3     | Gamma(4.4903452, 0.0290352)     | 13.37659 |    18.30704     |

: Distributions for each ASA Score

### Consult Duration

| ASA Score |          Distribution           |  Error   | Critical Values |
|:---------:|:-------------------------------:|:--------:|:---------------:|
|     1     | Lognormal(2.4525327, 0.8756247) | 9.605517 |    15.50731     |
|     2     |          Exp(0.048233)          |  5.7713  |    5.991465     |
|     3     | Lognormal(3.0657644, 0.8372545) | 5.50356  |    12.59159     |
|           |  Gamma(0.92089709, 0.03126416)  | 5.842161 |    5.991465     |
|           |         Exp(0.03394968)         | 4.483978 |    7.814728     |

: Distributions for each ASA Score

\newpage

## Planned Appointments

### Queue Time

| ASA Score |          Distribution           |  Error   | Critical Values |
|:---------:|:-------------------------------:|:--------:|:---------------:|
|     1     | Lognormal(4.7362772, 0.4766837) | 5.192523 |    9.487729     |
|     2     |   Gamma(4.6350196, 0.0309402)   | 20.84311 |    21.02607     |
|     3     |  Gamma(4.77692467, 0.03145134)  | 13.61228 |    14.06714     |

: Distributions for each ASA Score

### Consult Duration

| ASA Score |          Distribution           |  Error   | Critical Values |
|:---------:|:-------------------------------:|:--------:|:---------------:|
|     1     |  Lognormal(2.456952, 0.874598)  | 16.66601 |    16.91898     |
|           |   Gamma(0.7716552, 0.0479119)   | 13.26114 |    14.06714     |
|     2     |   Gamma(0.9400198, 0.0453387)   | 5.40839  |    5.991465     |
|           |         Exp(0.04823165)         | 11.10927 |    12.59159     |
|     3     | Lognormal(3.0717530, 0.8440134) | 4.778335 |    7.814728     |
|           |  Gamma(0.90118456, 0.03022804)  | 8.379399 |    9.487729     |
|           |         Exp(0.03354257)         | 6.057588 |     11.0705     |

: Distributions for each ASA Score

\newpage

## Walk-In Appointments

### Queue Time

| ASA Score |          Distribution           |  Error   | Critical Values |
|:---------:|:-------------------------------:|:--------:|:---------------:|
|     1     | Lognormal(4.8384769, 0.5555817) | 5.394277 |    9.487729     |
|           |  Gamma(2.76537723, 0.01876737)  | 2.535864 |    7.814728     |
|     2     |  Gamma(3.69937258, 0.02254071)  | 21.08321 |    22.36203     |
|           |  Lognormal(4.980962, 0.489148)  | 18.26444 |    22.36203     |
|     3     |  Gamma(3.50311077, 0.01894881)  | 7.495405 |    14.06714     |

: Distributions for each ASA Score

### Consult Duration

| ASA Score |          Distribution           |   Error   | Critical Values |
|:---------:|:-------------------------------:|:---------:|:---------------:|
|     1     | Lognormal(2.4071329, 0.8858606) | 0.8173222 |    7.814728     |
|           |  Gamma(0.74003981, 0.04794076)  | 12.19202  |    15.50731     |
|           |         Exp(0.06478132)         | 10.57594  |     11.0705     |
|     2     |  Lognormal(2.692986, 0.878081)  | 11.18576  |    12.59159     |
|           |  Gamma(0.78319684, 0.03778855)  | 4.265961  |    9.487729     |
|           |         Exp(0.0482491)          | 4.463257  |    12.59159     |
|     3     | Lognormal(3.0349670, 0.6988318) | 2.577932  |    7.814728     |
|           |  Gamma(1.47081119, 0.05755881)  | 2.209917  |    9.487729     |
|           |         Exp(0.03913405)         | 6.167518  |     11.0705     |

: Distributions for each ASA Score


```{r}

```

