---
title: "Amount of Time Being Served in PAC (Appointments)"
subtitle: "2019"
date: "Friday, 2 April 2021"
author: "Vincent Leonardo"
output:
  pdf_document:
    highlight: pygments
    latex_engine: xelatex
    number_sections: true
    toc: false
fontsize: 11pt
geometry: margin=1in
mainfont: STIX Two Text
mathfont: STIX Two Math
monofont: Fira Code
---

```{r include=FALSE}
# knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# Remove all variables from the R environment to create a fresh start
rm(list=ls())
# Execute our custom script for loading packages
source("usePackages.R")
# Name of the packages 
pkgnames <- c("ggplot2","dplyr","GGally","fmsb","tidyverse","knitr","lubridate",
              "patchwork", "fitdistrplus")
# Use our custom load function
loadPkgs(pkgnames)

source("2019_PAC_initial_cleaner.R")
source("histogram_maker.R")
source("cf_graph.R")
source("find_dist.R")
```

```{r include=FALSE}
planned_2019 <- PAC_initial_cleaner("Unedited CSV/2019_planned.csv")
# head(planned_2019)
```

Some things to note:

-   Not sure if total duration as denoted by the difference between `PAC Registration Time` and `PAC End Time` is a better fit than the `PAC Consult Duration`.
-   Hence, both distributions are included.
-   We are also looking preliminarily into other histograms, though we are not sure what to use it for yet.
-   `PAC Consult Duration` is for $\geq$ 15 minutes, then translated to start at 0 instead for CF and exponential. Gamma is not translated. \textbf{Not sure if this is correct.}
-   We should decide on whether to split based on ASA, Department or both.

Some questions:

-   Clarify that:
    -   Visit time = time allocated
    -   Listing date = when did they set the consult timing
    -   Register time = when did they come
    -   End time = when did they leave
    -   Consult duration = how long to consult per se

-   Department names:
    -   e.g. DDR/HPB is it the same as HPB?
    -   e.g. H&N ENT is it the same as ENT?
    -   Maybe can have a brief explanation so that we can try to cluster things

-   How was PAC registration/end time calculated?

# Histograms

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.keep='all'}
histogram_maker(planned_2019)
```

# Cullen and Frey Graphs

In order of:

1.  `PAC_to_listing_days`
2.  `PAC_consult_duration`
3.  `PAC_duration_total`
4.  `surgery_lead_time`

```{r echo=FALSE}
cf_graph(planned_2019)
```

# Distribution for Consult Duration

\textbf{Disclaimer}: distributions are not validated by chi-squared test yet but through other tests. Will need to ask James about these too. Will do the chi-squared tests soon.


## Exponential Fit (PAC Consult Duration Adjusted)
```{r echo=FALSE, warning=FALSE}
planned_2019_modified <- planned_2019 %>% 
  filter(PAC_consult_duration >= 15) %>% 
  mutate(PAC_consult_duration = PAC_consult_duration - 15)

find_dist(planned_2019_modified$PAC_consult_duration, "exp")
```
## Gamma Distribution (Not Adjusted)
```{r echo=FALSE, warning=FALSE}
planned_2019_modified_a <- planned_2019 %>% 
  filter(PAC_consult_duration >= 15)
find_dist(planned_2019_modified_a$PAC_consult_duration, "gamma")
```


# Distribution for Total Duration

\textbf{Disclaimer}: distributions are not validated by chi-squared test yet but through other tests. Will need to ask James about these too. Will do the chi-squared tests soon.

```{r echo=FALSE, warning=FALSE}
find_dist(planned_2019$PAC_duration_total, "gamma")
```
# Splitting by ASA

## Consult Duration

### Exponential
```{r echo=FALSE, warning=FALSE}
planned_2019_modified_1 <- planned_2019_modified %>% filter(asa == "1")
planned_2019_modified_2 <- planned_2019_modified %>% filter(asa == "2")
planned_2019_modified_3 <- planned_2019_modified %>% filter(asa == "3")
planned_2019_modified_4 <- planned_2019_modified %>% filter(asa == "4")

find_dist(planned_2019_modified_1$PAC_consult_duration, "exp")
find_dist(planned_2019_modified_2$PAC_consult_duration, "exp")
find_dist(planned_2019_modified_3$PAC_consult_duration, "exp")
find_dist(planned_2019_modified_4$PAC_consult_duration, "exp")
```
### Gamma
```{r echo=FALSE, warning=FALSE}
planned_2019_modified_a_1 <- planned_2019_modified_a %>% filter(asa == "1")
planned_2019_modified_a_2 <- planned_2019_modified_a %>% filter(asa == "2")
planned_2019_modified_a_3 <- planned_2019_modified_a %>% filter(asa == "3")
planned_2019_modified_a_4 <- planned_2019_modified_a %>% filter(asa == "4")

find_dist(planned_2019_modified_a_1$PAC_consult_duration, "gamma")
find_dist(planned_2019_modified_a_2$PAC_consult_duration, "gamma")
find_dist(planned_2019_modified_a_3$PAC_consult_duration, "gamma")
find_dist(planned_2019_modified_a_4$PAC_consult_duration, "gamma")
```

