---
title: "Amount of Time Being Served in PAC (Appointments)"
subtitle: "2020"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Vincent Leonardo"
output:
  pdf_document:
    highlight: pygments
    latex_engine: xelatex
    number_sections: true
    toc: false
fontsize: 11pt
geometry: margin=1in
mainfont: STIX Two Text
mathfont: STIX Two Math
monofont: Fira Code
---

```{r include=FALSE}
# knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# Remove all variables from the R environment to create a fresh start
rm(list=ls())
# Execute our custom script for loading packages
source("Functions/usePackages.R")
# Name of the packages 
pkgnames <- c("ggplot2","dplyr","GGally","fmsb","tidyverse","knitr","lubridate",
              "patchwork", "fitdistrplus")
# Use our custom load function
loadPkgs(pkgnames)

source("Functions/2020_PAC_initial_cleaner.R")
source("Functions/histogram_maker.R")
source("Functions/cf_graph.R")
source("Functions/find_dist.R")
source("Functions/chi_squared_exp.R")
source("Functions/chi_squared_gamma.R")
```

```{r include=FALSE}
planned_2020 <- PAC_initial_cleaner("Unedited CSV/2020_planned.csv")
# head(planned_2020)
```

**Some things to note:**

-   Not sure if total duration as denoted by the difference between `PAC Registration Time` and `PAC End Time` is a better fit than the `PAC Consult Duration`. Question for SGH.
-   Hence, both distributions are included.
-   We are also looking preliminarily into other histograms, though we are not sure what to use it for yet.
-   `PAC Consult Duration` is for $\geq$ 15 minutes, then translated to start at 0 instead for initial histogram, CF and exponential parameter approximation. Gamma is not translated. \textbf{Not sure if this is correct.}
-   We should decide on whether to split based on ASA, Department or both.

\textbf{Disclaimer}: Some distributions are not validated by chi-squared test yet but through other tests. Will do the chi-squared tests soon.

\textbf{Chi-squared tests at $\alpha=0.05$.}

<!--Some questions:

-   Clarify that:
    -   Visit time = time allocated
    -   Listing date = when did they set the consult timing
    -   Register time = when did they come
    -   End time = when did they leave
    -   Consult duration = how long to consult per se

-   Department names:
    -   e.g. DDR/HPB is it the same as HPB?
    -   e.g. H&N ENT is it the same as ENT?
    -   Maybe can have a brief explanation so that we can try to cluster things

-   How was PAC registration/end time calculated?-->

\newpage

# Histograms

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.keep='all'}
histogram_maker(planned_2020)
```

# Cullen and Frey Graphs

In order of:

1.  `PAC_to_listing_days`
2.  `PAC_consult_duration`
3.  `PAC_duration_total`
4.  `surgery_lead_time`

```{r echo=FALSE}
cf_graph(planned_2020)
```

# Distribution for Consult Duration


## Exponential Fit (PAC Consult Duration Adjusted)
```{r echo=FALSE, warning=FALSE}
planned_2020_modified <- planned_2020 %>% 
  filter(PAC_consult_duration >= 15) %>% 
  mutate(PAC_consult_duration = PAC_consult_duration - 15)

planned_2020_modified <- 
  planned_2020_modified[!is.na(planned_2020_modified$PAC_consult_duration),]

find_dist(planned_2020_modified$PAC_consult_duration, "exp")

kable(
  chi_squared_exp(planned_2020_modified,
                planned_2020_modified$PAC_consult_duration,
                c(0,25,50,75,100,125,150,175,200,225,10000),
                0.04995227),
  caption = "Chi-Squared Test for Exponential Distribution"
)

```
## Gamma Distribution (Not Adjusted)
```{r echo=FALSE, warning=FALSE}
planned_2020_modified_a <- planned_2020 %>% 
  filter(PAC_consult_duration >= 15)
find_dist(planned_2020_modified_a$PAC_consult_duration, "gamma")

planned_2020_modified_a <- 
  planned_2020_modified_a[!is.na(planned_2020_modified_a$PAC_consult_duration),]

kable(
  chi_squared_gamma(planned_2020_modified_a,
                planned_2020_modified_a$PAC_consult_duration,
                c(0,25,50,75,100,125,150,175,200,225,10000),
                3.9019472,
                0.1114137),
  caption = "Chi-Squared Test for Gamma Distribution"
)
```


# Distribution for Total Duration

```{r echo=FALSE, warning=FALSE}
find_dist(planned_2020$PAC_duration_total, "gamma")

planned_2020_total_duration_na <- 
  planned_2020[!is.na(planned_2020$PAC_duration_total),] %>% 
  mutate(PAC_duration_total = as.integer(PAC_duration_total)) %>% 
  filter(PAC_duration_total > 0)

kable(
  chi_squared_gamma(planned_2020_total_duration_na,
                planned_2020_total_duration_na$PAC_duration_total,
                c(0,20,40,60,80,100,120,140,160,180,200,220,240,260,280,300,320,
                  340,360,380,400,420,440,460,480,500,550,10000),
                4.56048704,
                0.02781078),
  caption = "Chi-Squared Test for Gamma Distribution"
)
```
# Splitting by ASA

## Consult Duration

```{r echo=FALSE}
planned_2020_modified_a_1 <- planned_2020_modified_a %>% filter(asa == "1")
planned_2020_modified_a_2 <- planned_2020_modified_a %>% filter(asa == "2")
planned_2020_modified_a_3 <- planned_2020_modified_a %>% filter(asa == "3")
planned_2020_modified_a_4 <- planned_2020_modified_a %>% filter(asa == "4")

mean_1 <- mean(planned_2020_modified_a_1$PAC_consult_duration)
mean_2 <- mean(planned_2020_modified_a_2$PAC_consult_duration)
mean_3 <- mean(planned_2020_modified_a_3$PAC_consult_duration)
mean_4 <- 0

mean_asa <- tibble(
  ASA = c(1:4),
  Average = c(mean_1,mean_2,mean_3,mean_4)
)

ggplot(mean_asa) + geom_col(aes(ASA,Average)) +
  labs(
    title = "Average Consult Duration",
    subtitle = "For ASA 1, 2, 3 and 4",
    caption = "For ASA 4, the value is zero",
    x = "ASA Score",
    y = "Average Consult Duration"
  )
```


### Exponential
```{r echo=FALSE, warning=FALSE}
planned_2020_modified_1 <- planned_2020_modified %>% filter(asa == "1")
planned_2020_modified_2 <- planned_2020_modified %>% filter(asa == "2")
planned_2020_modified_3 <- planned_2020_modified %>% filter(asa == "3")
# planned_2020_modified_4 <- planned_2020_modified %>% filter(asa == "4")

find_dist(planned_2020_modified_1$PAC_consult_duration, "exp")
find_dist(planned_2020_modified_2$PAC_consult_duration, "exp")
find_dist(planned_2020_modified_3$PAC_consult_duration, "exp")
# find_dist(planned_2020_modified_4$PAC_consult_duration, "exp")
```
### Gamma
```{r echo=FALSE, warning=FALSE}
find_dist(planned_2020_modified_a_1$PAC_consult_duration, "gamma")
find_dist(planned_2020_modified_a_2$PAC_consult_duration, "gamma")
find_dist(planned_2020_modified_a_3$PAC_consult_duration, "gamma")
# find_dist(planned_2020_modified_a_4$PAC_consult_duration, "gamma")
```

